# Visual Acuity

```{r}
library(data.table)
```

Suppose we are interested in the hypothesis that children playing outside leads them to have better eyesight.

Consider the following population of ten children whose visual acuity we can measure.

-   Visual acuity is the decimal version of the fraction given as output in standard eye exams.
-   Someone with 20/20 vision has acuity 1.0, while someone with 20/40 vision has acuity 0.5.
-   Numbers greater than 1.0 are possible for people with better than “normal” visual acuity.

```{r make visual data}
d <- data.table(
  child = 1:10, 
  y_0 = c(1.2, 0.1, 0.5, 0.8, 1.5, 2.0, 1.3, 0.7, 1.1, 1.4), 
  y_1 = c(1.2, 0.7, 0.5, 0.8, 0.6, 2.0, 1.3, 0.7, 1.1, 1.4)
)
```

In this table:

-   `y_1` means the measured *visual acuity* if the child were to play outside at least 10 hours per week from ages 3 to 6\
-   `y_0` means the measured *visual acuity* if the child were to play outside fewer than 10 hours per week from age 3 to age 6;
-   Both of these potential outcomes *at the child level* would be measured at the same time, when the child is 6.

## Treatment effect

Compute the individual treatment effect for each of the ten children.

```{r, include = TRUE}
# Use this code chunk to show your code work

```

## Story time

Tell a "story" that could explain this distribution of treatment effects. In particular, discuss what might cause some children to have different treatment effects than others.

```{r, include = TRUE}
# Use this code chunk to show your code work (if needed)

```

**Answer:** ...

## True ATE

For this population, what is the true average treatment effect (ATE) of playing outside.

```{r, include = TRUE}
# Use this code chunk to show your code work

```

**Answer:** ...

## Even-Odd split

Suppose we are able to do an experiment in which we can control the amount of time these children play outside for three years. We happen to randomly assign the odd-numbered children to treatment and the even-numbered children to control. What is the estimate of the ATE you would reach under this assignment? (Please describe your work.)

```{r, include = TRUE}
# Use this code chunk to show your code work

```

**Answer:** ...

## Biased or Unbiased?

How different is the estimate from the truth? In your own words, why is there a difference? Does this mean that the estimator is a biased or an unbiased estimator? Does this mean that the estimate is biased or unbiased?

```{r, include = TRUE}
# Use this code chunk to show your code work

```

**Answer:** ...

## How many splits are possible?

We just considered one way (odd-even) an experiment might split the children. How many different ways (every possible way) are there to split the children into a treatment versus a control group (assuming at least one person is always in the treatment group and at least one person is always in the control group)?

```{r, include = TRUE}
# Use this code chunk to show your code work

```

**Answer:** ...

## Think about your assignment strategy

Given there are as many ways to assign as you answered in the last sub-question, can you provide a rationale for why you might prefer one assignment strategy over another?

For concreteness, suppose that either (a) you can have a treatment assignment where one and only one of the kids is randomly assigned to treatment; or (b) you can have a treatment assignment where exactly five of the kids are randomly assigned to treatment.

As a small hint, you might note that $\left\{\left[\displaystyle\sum_{i=1}^{n}Y_{i}(1)|d_{i}=1\right] - \left[\displaystyle\sum_{j=1}^{n}Y_{j}(0)|d_{j} = 0 \right]\right\} \equiv ATE$ is an estimator and there are some properties of estimators that we care about.

To make the question tractable, suppose that if you were to increase the size of the population procedure (a) would keep a single kid in treatment, while procedure (b) would keep 50% of the sample in treatment and 50% of the sample in control.

## Compute the MSE of these two designs

Because you have the entire population of kids, their entire scheduled of potential outcomes, and and two proposed sampling procedures: conduct a simulation study. First, calculate all of the possible treatment effects that you might observe under each design. Then, compute the mean-squared error of each design. Which design -- the one where you have a single kid in treatment, or the one where you have five kids in treatment -- produces a lower MSE? (Hint the `combn` function might help you with your subsetting.)

## Observational study

Suppose that we decide it is too hard to control the behavior of the children, so we do an observational study instead. Children 1-5 choose to play an average of more than 10 hours per week from age 3 to age 6, while Children 6-10 play less than 10 hours per week. Compute the difference in means from the resulting observational data.

```{r, include = TRUE}
# Use this code chunk to show your code work

```

**Answer:** ...

## Observational ATE

Compare your answer in `Observational study` to the true ATE. In your own words what causes the difference? Does this mean that the estimator is a biased or an unbiased estimator? Does this mean that the estimate is biased or unbiased?

```{r, include = TRUE}
# Use this code chunk to show your code work (if needed)

```

**Answer:** ...
